---
title: "hw03"
output: github_document
---

```{r}
suppressPackageStartupMessages(require(gapminder))
head(gapminder)
```
Maximum gpd per capita for all continents
```{r}
range(gapminder$gdpPercap)
```
Spread of gdp per capita within continents
```{r}
suppressPackageStartupMessages(require(tidyverse))
suppressPackageStartupMessages(require(dplyr))
for (cont in unique(gapminder$continent)) {
  print(paste(cont," has min and max",toString(range(filter(gapminder,continent==cont)$gdpPercap))))
}
```
Life Expectancy weighted by population
```{r}
print(paste("lifeExp weigthed by pop is",mean(gapminder$lifeExp*gapminder$pop)))
```
Mean lifeExp at 1995 is
```{r}
print(paste("mean lifeExp in 1952 is",mean(filter(gapminder,year==1952)$lifeExp)))
```
Change of lifeExp over years for each continent
```{r}
yvsl = ggplot(gapminder, aes(year,lifeExp))
yvsl + geom_point() + facet_wrap(~continent)
```

Scatterplot of countries with low lifeExp. By low lifeExp I mean lifeExp < 40
```{r}
CUT_OFF = 40
gapminder %>% 
  filter(lifeExp < CUT_OFF) %>% 
  ggplot(aes(year, lifeExp)) + geom_point()
```
Count exact number of such countires. Clearly it is decreasing.
```{r}
gapminder %>%
  filter(lifeExp < CUT_OFF) %>%
  group_by(year) %>%
  tally() %>% 
  ggplot(aes(x = year, y = n)) + geom_line()
```

Story: 
Find out the count countries when gdp drops sharply, and visualize by year. Search what happened in those years. For example, was there a war at that time?



